---
title: "Gmail_Study"
author: "Patience Heath"
date: "2025-09-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

# Gmail Usability Testing Graphs 

```{r dataframe, echo = FALSE}
#0 means struggled in task 1 means completed task with ease
#0 is no and 1 is yes 

gmail_data = data.frame(participants = c("Dajah", "Chris", "Darius", "Nate"),
                  stars_features = c(0,0,0,0),
                  save_changes = c(0,0,0,1),
                  learn_more_preference = c("centered pop-up", "centered pop-up", "seperate tab", "side panel"),
                  like_vacation_responder = c(1,1,1,0),
                  desktop_notifications = c(1,1,1,1),
                  layout_changes = c(1,1,1,0))

gmail_data = gmail_data %>% mutate(across(c(stars_features, save_changes, like_vacation_responder, desktop_notifications, layout_changes), ~ as.factor(.x)))

write.csv(gmail_data, "/Users/patienceheath/gmail_data.csv", row.names = FALSE)

                  
```

### Save Changes Task Pie Chart 

Participants that were able to complete a given task and save changes without being probed to do so.

```{r barplot save changes task, echo = FALSE}

gmail_data %>% count(save_changes) %>%
  ggplot(aes(x = "", y = n, fill = save_changes)) + geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  theme_void() +
  labs(fill = "Completed Save Changes Task",
       title = "Save Changes Task")
```

### Stars Features Task Pie Chart

Participants were asked to explain what the stars features was according to the description provided in settings.

```{r stars feature task, echo = FALSE}
gmail_data %>% count(stars_features) %>% 
  ggplot(aes(x = "", y = n, fill = stars_features)) + geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  theme_void() +
    labs(fill = "Completed Stars Task",
         title = "Stars Feature Task")
```

### Desktop Notifications Task Pie Chart

Participants were given a scenario where they would have to locate desktop notifications in Gmail.

```{r desktop notifications, echo = FALSE}
gmail_data %>% count(desktop_notifications) %>% 
  ggplot(aes(x = "", y = n, fill = desktop_notifications)) + geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  theme_void() +
    labs(fill = "Completed Desktop Notifications Task",
         title = "Desktop Notifications Task")

```

### Desktop Notifications Task Pie Chart

Participants were shown 3 different ways that gmail presents information after clicking *learn more*. They were asked which presentation method they preferred the most. 

```{r learn more preference, echo = FALSE}


gmail_data %>% ggplot(aes(x = learn_more_preference)) + geom_bar(fill = "salmon") +
  labs(title = "Learn More Presentation Preferences",
       x = "Learn More Preference")

  
```
### Layout Changes 

Participants that suggested that the layout needs to change after testing. 

```{r layout changes, echo = FALSE}


gmail_data %>% ggplot(aes(x = layout_changes)) + geom_bar(fill = "salmon") +
  labs(title = "Participants Suggesting Layout Changes",
       x = " Layout changes")

```

